---
title: "Toolkit latest and previous raw wave comparison"
output:
  html_document: default
    df_print: paged
---

Uses comparedf from arsenal package - https://cran.r-project.org/web/packages/arsenal/vignettes/comparedf.html#example-1 

Execute this chunk by clicking the *Run* arrow button within the chunk or by placing your cursor inside it/highlighting relevant code and pressing *Ctrl+Shift+Enter*.

Remember to update the file path for the 'previous' and 'latest' wave data before running code chunk.

OUTPUT UNDER CODE CHUNK
Box 1 = Summary of data frames (number of cases and variables)
Box 3 = Summary of comparison (Number of variables that are not in each dataset)
Box 4 = Variables not shared and which wave they are present in (x = latest, y = previous)
Box 9 = Non-identical attributes (indicates if variables have differences and what the difference is (e.g. label, class etc...))

```{r}
library(haven)
library(arsenal)

# Read in data

previous <- read_sav("C:/Toolkit merge files/Waves/187/21-087517-18 ST TA Wave 187 SPSS_v1_internal.sav")
latest <- read_sav("C:/Toolkit merge files/Waves/188/21-087517-22 ST TA Wave 188 SPSS_v1_internal.sav")

# 12 month re-contact
recontact_prev <- read_sav("C:/Toolkit merge files/Waves/187/Recontact/20-087517-18 ST TA Wave 92 SPSS-v1_internal.sav")
recontact_lat <- read_sav("C:/Toolkit merge files/Waves/188/Recontact/20-087517-22 ST TA Wave 93 SPSS-v1_internal.sav")

# At bottom of output see "Table: Non-identical attributes". Indicates if variables have differences.
# Name column indicates what the difference is (i.e. label, levels or class)
print(summary(comparedf(previous, latest)))

print(summary(comparedf(sts_t, sts_f)))
```


```{r}
# Recontact
print(summary(comparedf(recontact_prev, recontact_lat)))
```


Assess variable attributes
```{r}

attributes(latest$q632a45) # Pouch
attributes(latest$q632e24)
attributes(latest$neww53a_o)
attributes(latest$qimw8613)

attributes(latest$qaap1lp_10)

```

